Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-02-22 src/article.tex
Two additonal scaffolding references

Synteny methods compare the assembled contigs to a more complete reference
genome sequence searching for areas of sequence similarity between the two.
Areas of corresponding sequence between the the two sets are can be used to
infer contig placement and build the scaffold \cite{richter2007,zhao2008}.
Recombination between the two genomes can however reduce the effectiveness of
this analysis. \pb

@@

As mentioned above, the genome may be prepared prior to sequencing so that
reads are produced in pairs at a known distance. This paired-read data
provides an extra level of information on how contigs may be scaffolded
together. Heuristic graph algorithms may take advantage of this data to search
for optimal configuration of contigs in the scaffold using paired-read distances
\cite{dayarian2010}. Additional data using a reference genome may also be
combined when estimating the best contig configuration \cite{pop2004}. Finally
when the scaffold cannot be completely resolved \emph{in silico} software
packages exist to suggest the likely primers necessary for PCR amplifying the
sequence in gap regions \cite{gordon2001,nagarajan2010}. \pb

>>>>

Synteny methods compare the assembled contigs to a more complete reference
genome sequence searching for areas of sequence similarity between the two.
Areas of corresponding sequence between the the two sets are can be used to
infer contig placement and build the scaffold
\cite{richter2007,zhao2008,assefa2009}. Recombination between the two genomes
can however reduce the effectiveness of this analysis. \pb

@@

As mentioned above, the genome may be prepared prior to sequencing so that
reads are produced in pairs at a known distance. This paired-read data
provides an extra level of information on how contigs may be scaffolded
together. Heuristic algorithms may take advantage of this data to search for
optimal configuration of contigs in the scaffold using paired-read distances
\cite{dayarian2010,boetzer2011}. Additional data using a reference genome may
also be combined when estimating the best contig configuration \cite{pop2004}.
Finally when the scaffold cannot be completely resolved \emph{in silico}
software packages exist to suggest the likely primers necessary for PCR
amplifying the sequence in gap regions \cite{gordon2001,nagarajan2010}. \pb
